Incentivizing Exploration with Heterogeneous Utilities

### 2017-11-27 paper.tex
Fix another minor issue in proof of Lemma 1
edits to language in proof of lemma 3

\begin{proof}
\begin{align*}
S(\delta)
&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})<\delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
&=M\delta.
\end{align*}
\end{proof}

@@

\begin{lemma}
For those user whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

In order to prove the original lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{4.8\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item $n\geq \frac{23.04\sigma^4}{\lambda^4}$ we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

@@

We also need to use an adaptive concentration inequality, which is introduce in \cite{zhao2016adaptive}. For reference, we state it as a Lemma.

@@

Now we can get back to prove Lemma~\ref{round:prob}.

\begin{proof}
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
\begin{align}
&P(\text{myopic action incurs regret})\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right). \label{ACI}
\end{align}

>>>>

\begin{proof}
\begin{align*}
S(\delta)
&=\sum_{i,j}P(\theta\cdot(u_{i}-u_{j})\le \delta|\theta\in \Omega_{i,j})P(\theta\in \Omega_{i,j}) \\
&\leq \sum_{i,j}M\delta \times P(\theta\in \Omega_{i,j}) \\
&=M\delta.
\end{align*}
\end{proof}

@@

\begin{lemma}
For those users whose utility difference between their best arm and the second best arm is at least $2m\lambda$, the probability that a myopic action can incur regret at any time $t\in [t_{n-1},t_{n}-1]$ in the $n^{th}$ round is bounded above by $24Nm\exp\left(-\frac{1.8n\lambda^2}{8\sigma^2}\right)$, for $n\geq n_{0}=\max\{50, \frac{23.04\sigma^4}{\lambda^4}\}$.
\label{round:prob}
\end{lemma}

@@

To prove the lemma, we just need to show for $n\geq n_{0}$, we have
\begin{align}
\frac{n}{3+\log(n)}\geq \frac{4.8\sigma^2}{\lambda^2}. \label{n0-equ}
\end{align}
Inequality~(\ref{n0-equ}) is true because of the following two observations:
\begin{itemize}
\item for $n\geq 50$, we have $\frac{n}{3+\log(n)}\geq n^{0.5}$;
\item for $n\geq \frac{23.04\sigma^4}{\lambda^4}$, we have $n^{0.5}\geq {4.8\sigma^{2}}{\lambda^{2}}$.
\end{itemize}

@@

To prove Lemma~\ref{round:prob}, we also need to use an adaptive concentration inequality due to \cite{zhao2016adaptive}. For reference, we state it here as a Lemma.

@@

We now prove Lemma~\ref{round:prob}.

\begin{proof}[Proof of Lemma~\ref{round:prob}]
In the $n^{th}$ round, we know all arms have been pulled at least $n$ times. Thus, the probability that myopic action can occur regret is bounded by
\begin{align}
&P(\text{myopic action incurs regret})\nonumber \\
\leq &P(\exists i, \exists j, |u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
\leq & \sum_{i}\sum_{j} P(|u_{i,t}^{j}-u_{i}^{j}|>\lambda) \nonumber \\
= &  \sum_{i}\sum_{j} P\left(\bigg|\sum_{k\in \tau_{i,t}}\epsilon_{k}\bigg|>N(i,t)\lambda\right). \label{ACI}
\end{align}
